\subsection{Git Forks}
Git Fork is an unique feature of GitHub. First version of Translator translates Git Fork and pull request using Subversion concepts of copy and merge,
but makes not attempt to represent Subversion operations as a Git Fork.\\\\
Further versions of Translator might extend translation
rules so that some specific copies and merges performed in Subversion repository are translated into Git Fork.

\subsubsection{Forked Repository}
Git Repository Fork creates new Git repository on GitHub. This new forked Git repository has the following 
important features:
\begin{itemize}
\item Repository is assigned to a particular \emph{user}
\item Repository holds information on its \emph{origin} and includes complete origin history
\item Changes made in the forked repository might be \emph{pulled back} into origin repository
\end{itemize}

These features make its natural to translate Git Fork into a copy \emph{within} Subversion repository. Single fork 
operation is translated into a revision which copies Subversion repository top-level directories into another top-level directory. 
Thus, fork performed by the \emph{user} will be translated into the following revision:\\

rN user\\ 
=======================\\
Fork comment             \\
=======================\\
A /\emph{user}/trunk copied from /trunk at rM\\
A /\emph{user}/branches copied from /branches at rM\\
A /\emph{user}/tags copied from /tags at rM\\\\

Repository layout after the fork:\\

/trunk\\
/branches\\
/tags\\
/\emph{user}/trunk\\
/\emph{user}/branches\\
/\emph{user}/tags\\\\

Certain limitations are enforces on the fork /\emph{user} directory - similar to the other top-level directories it might not be 
copied or deleted. Subdirectories of /\emph{user} directory are subjects to the same limitations that are described in the "Fixed Repository Layout" section
and additionally subdirectories of /\emph{user} directory might not be copied to the locations outside of the /\emph{user} directory.
\\\\
Changes made by Subversion users to the files and directories in /\emph{user} directory are translated to the Git commits in the forked Git
repository and vice versa - Git commits in the forked Git repository are translated into Subversion revisions which modifies files
and directories in the corresponding /\emph{user} directory of Subversion repository.

\subsubsection{Pull Request}

Accepted Git pull request is represented as a Git commit(s) in the original Git repository. Those Git commits are translated into Subversion
revision using standard translation rules. Additionally, Translator updates merge tracking information on the affected branches, so that
from the Subversion user perspective, translated revision looks like a merge of changes from the corresponding branches in the /\emph{user} directory. 
Merge tracking information in Subversion repository after translation may look like:\\

/trunk : from /\emph{user}/trunk:10-11\\
/branches/b : from /\emph{user}/branches/b:10-11\\

assuming that revisions 10 and 11 represent changes in the forked Git repository.